Response to the defense feedback

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Independent Leakages}
If any observation of $A$ does not affect the probability of occurrence of any observation of $B$, we call the two leakage sites $A$ and $B$ are independent. $p_{ab} = p_ap_b$.
If $A$ and $B$ are two independent leakages, the total amount of leaked information is:
\begin{align*} 
L_{\mathit{AB}} &= - \sum_{}p_{ab}\log_2p_{ab} = - \sum_{}p_ap_b\log_2p_ap_b \\
                &= - \sum_{}p_{a}\log_2p_{a} - \sum_{}p_{b}\log_2p_{b} \\
                &= L_A + L_B
\end{align*}

>>>>

\subsection{Independent Leakages}
Given a leakage site $A$, the site has different memory access patterns under different secrets. We call each memory access pattern as an observation. If any observation of $A$ does not affect the probability of occurrence of any observation of $B$, we call the two leakage sites $A$ and $B$ are independent. $p_{ab} = p_ap_b$.
If $A$ and $B$ are two independent leakages, the total amount of leaked information is:
\begin{align*} 
L_{\mathit{AB}} &= - \sum_{}p_{ab}\log_2p_{ab} = - \sum_{}p_ap_b\log_2p_ap_b \\
                &= - \sum_{}p_{a}\log_2p_{a} - \sum_{}p_{b}\log_2p_{b} \\
                &= L_A + L_B
\end{align*}
